### 2016-05-12 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More edits

ggplot(dd,aes(y = CqTelomere, x = CqGAPDH,col = Ageclass))+
geom_point()+
stat_smooth(method = 'lm')

>>>>

ggplot(dd,aes(y = CqGAPDH, x = Agemonths,col=Sex))+
geom_point()+
stat_smooth(method = 'lm')

summary(lm(CqGAPDH~Agemonths,data=dd))
summary(lm(CqTelomere~Agemonths,data=dd))
summary(lm(RTL~Agemonths,data=dd))
